Simulating High-Dimensional Multivariate Data

### 2020-12-22 040-monte-carlo-evaluation.Rmd
4th draft. Remove latex styling

```{r ch040-LoadLib040, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
## devtools::install_github("SchisslerGroup/bigsimr", ref = 'develop')
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
## cores <- as.integer( 1 )
set.seed(10162020)
```

@@

```{r ch040-biMAEtable, results='asis', cache=F}
## tabMSE  <- allDat %>%
##    group_by( N, margins ) %>%
##    summarize( mse = mean( ( rho - rho_hat )^2 ) )
tabMSE  <- allDat %>%
    ## filter( N == 100000) %>%
    group_by( N, type, margins ) %>%
##     summarize( mse = mean( ( rho - rho_hat )^2 ) ) %>%
    summarize( MAE = mean( abs( rho - rho_hat )  ) )
## normMSE <- as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ] ) 
## ( tabMSE$mse - normMSE ) / normMSE
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) )
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) ) / tabMSE$mse

knitr::kable(tabMSE,
             format = 'latex',
             col.names = c("No. of random vectors",
                           "Correlation type",
                           "Distribution",
                           "Mean abs. error"),
             booktabs = TRUE,
             caption = 'Average abolute error in matching the target dependency across the entire range of possible correlations for each bivariate marginal.',
             linesep = c('', '',  '\\addlinespace')
)
```

Figure \@ref(fig:ch040-bPlot) displays the aggregated bivariate simulation results.
Table \@ref(tab:ch040-biMAEtable) contains the mean absolute error (MAE) in reproducing the desired dependency measures for the three bivariate scenarios.
Overall, the studies show that our methodology is generally accurate across the entire range of possible correlation values for the rank-based dependency measures, at least in these limited simulation settings for the rank-based correlations.
For the two non-normal bivariate marginals, the Pearson correlation matching is approximate.
For discrete margins, matching the dependency measures was somewhat less accurate, even for the rank-based metrics, and particularly inaccurate near the lower bound of Pearson correlations.

>>>>

```{r ch040-LoadLib040, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide"}
## devtools::install_github("SchisslerGroup/bigsimr", ref = 'develop')
## knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
## cores <- as.integer( 1 )
set.seed(10162020)
```

@@

Figure \@ref(fig:ch040-bPlot) displays the aggregated bivariate simulation results.
Table \@ref(tab:ch040-BiError) contains the mean absolute error (MAE) in reproducing the desired dependency measures for the three bivariate scenarios.

```{r ch040-BiError, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
## tabMSE  <- allDat %>%
##    group_by( N, margins ) %>%
##    summarize( mse = mean( ( rho - rho_hat )^2 ) )
tabMAE  <- allDat %>%
    ## filter( N == 100000) %>%
    group_by( N, type, margins ) %>%
##     summarize( mse = mean( ( rho - rho_hat )^2 ) ) %>%
    summarize( MAE = mean( abs( rho - rho_hat )  ) )
## normMSE <- as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ] ) 
## ( tabMSE$mse - normMSE ) / normMSE
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) )
## ( tabMSE$mse - as.numeric( tabMSE[ tabMSE$margins == 'norm', 'mse' ]) ) / tabMSE$mse

## AGS 12/22/20: Removing the latex formating fixes the html render.
## But how to improve latex table formating? Better to use the template
knitr::kable(tabMAE,
             ## format = 'latex',
             col.names = c("No. of random vectors",
                           "Correlation type",
                           "Distribution",
                           "Mean abs. error"),
             ## booktabs = TRUE,
             caption = 'Average abolute error in matching the target dependency across the entire range of possible correlations for each bivariate marginal.',
             ## linesep = c('', '',  '\\addlinespace')
)
```

Overall, the studies show that our methodology is generally accurate across the entire range of possible correlation values for the rank-based dependency measures, at least in these limited simulation settings for the rank-based correlations.
For the two non-normal bivariate marginals, the Pearson correlation matching is approximate.
For discrete margins, matching the dependency measures was somewhat less accurate, even for the rank-based metrics, and particularly inaccurate near the lower bound of Pearson correlations.
